Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-22 Draft.Rmd
moved code

# take top 20 important variables
import20 = import[1:20,]

# Use Information Gain for variable selection
library(MASS)

fit_lm = lm(value~, data=train)

stepAIC(fit_lm, direction="backward", trace=FALSE)
stepAIC(fit_lm, direction="forward", trace=FALSE)
stepAIC(fit_lm, direction="both", trace=FALSE)

# Use Recursive Feature Elimination method
set.seed(123)
cparam = rfeControl(functions=lmFuncs, method='repeatedcv', repeats=5, number=10, verbose=FALSE, returnResamp='all')

profile=rfe(x=train_scaled, y=as.matrix(train$value), sizes=c(1:20),rfeControl=cparam)

# Use Lasso for variable selection X
y=train[,2]

library(glmnet)
feat_mod_select = cv.glmnet(train_scaled, train$value, standardize=TRUE, alpha=1)

as.matrix(coef(features,features$lambda.min))

# Scale dataset

# Covar. matrix

# Eigenval.s and eigenvec.s

# PCA

# Data transformation in new dimensional space

## Models 
```{r}
set.seed(123)
library(party)
# fit randfom forest and get var. importance based on mean decr. in accuracy
train_num = train[,2:50] |> dplyr::select(where(is.numeric))
cf1 = cforest(value ~ ., data=train_num, control=cforest_unbiased(mtry=2, ntree=50))
# adj for corr. btw predictors
varimp(cf1, conditional=TRUE)
# more robust towards class imbalance
varimpAUC(cf1)

```{r Lin Regr.}
model1 <- linear_reg() %>% 
    set_engine("lm") %>% 
    set_mode("regression")

>>>>

# take top 20 important variables
import20 = import[1:20,]
```

```{r delete}
# Use Information Gain for variable selection
library(MASS)
fit_lm = lm(value~, data=train)
stepAIC(fit_lm, direction="backward", trace=FALSE)
stepAIC(fit_lm, direction="forward", trace=FALSE)
stepAIC(fit_lm, direction="both", trace=FALSE)

# Use Recursive Feature Elimination method
set.seed(123)
cparam = rfeControl(functions=lmFuncs, method='repeatedcv', repeats=5, number=10, verbose=FALSE, returnResamp='all')
profile=rfe(x=train_scaled, y=as.matrix(train$value), sizes=c(1:20),rfeControl=cparam)

# Use Lasso for variable selection X
y=train[,2]
library(glmnet)
feat_mod_select = cv.glmnet(train_scaled, train$value, standardize=TRUE, alpha=1)
as.matrix(coef(features,features$lambda.min))

# fit randfom forest and get var. importance based on mean decr. in accuracy
set.seed(123)
library(party)
train_num = train[,2:50] |> dplyr::select(where(is.numeric))
cf1 = cforest(value ~ ., data=train_num, control=cforest_unbiased(mtry=2, ntree=50))
# adj for corr. btw predictors
varimp(cf1, conditional=TRUE)
# more robust towards class imbalance
varimpAUC(cf1)

# Scale dataset
# Covar. matrix
# Eigenval.s and eigenvec.s
# PCA
# Data transformation in new dimensional space
```

## Models 
```{r Lin Regr.}
model1 <- linear_reg() %>% 
    set_engine("lm") %>% 
    set_mode("regression")
